---
title: "RP- Childcare"
author: "Sonam Motiani"
date: "11/29/2020"
output:
  html_document: default
  pdf_document: default
---





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("easypackages")
easypackages::packages("data.table", "DT", "dplyr", "mgcv", "ggplot2", "RColorBrewer", "plotly", "parallel", "summarytools", "mltools", prompt = F)
```
```{r}
#reading file combinedprcf
Combinedprcf <- fread("//Users/sonammotiani/Downloads/Combinedprcf.csv")
```


```{r}

  Q_1_5 <- Combinedprcf %>% 
  filter (Q == 1) %>%
  group_by(YEAR99) %>% 
  summarise(Q_1_5_PR = weighted.mean(Y3,ICSWT26))

  ROC_1_5 <- Combinedprcf %>% 
  filter (Q == 0) %>%
  group_by(YEAR99) %>% 
  summarise(ROC_1_5_PR = weighted.mean(Y3,ICSWT26))

  PR <- left_join( Q_1_5, ROC_1_5, by='YEAR99')
  

  
PR_Plot <- ggplot(data = PR, aes(x=YEAR99))+ geom_point(aes(y = ROC_1_5_PR,col = "RoC 1-5 years > 0"), fill = "blue", shape = 25, size = 2) +  geom_line(aes(y = ROC_1_5_PR,col = "RoC 1-5 years > 0")) + geom_point(aes(y = Q_1_5_PR,col = "Q 1-5 years > 0"), fill = "magenta", shape = 22, size = 2) +  geom_line(aes(y = Q_1_5_PR,col = "Q 1-5 years > 0"))+ scale_color_manual( values = c( "magenta","blue"))+labs(title = "Mother's Labor Force Participation", subtitle = "1996 to 2010", x = "Year", y = "Mothers Employed") +  scale_x_continuous(breaks=seq(1996, 2010, 1))

PR_Plot

```
```{r}
  Q_1_5 <- Combinedprcf %>% 
  filter (Q == 1) %>%
  group_by(YEAR99) %>% 
  summarise(Q_1_5_QO = weighted.mean(Y3,ICSWT26))

  O_1_5 <- Combinedprcf %>% 
  filter (O == 1) %>%
  group_by(YEAR99) %>% 
  summarise(O_1_5_QO = weighted.mean(Y3,ICSWT26))

  QO <- left_join( Q_1_5, O_1_5, by='YEAR99')
  

  
QO_Plot <- ggplot(data = QO, aes(x=YEAR99))+ geom_point(aes(y = O_1_5_QO,col = "O 1-5 years > 0"), fill = "blue", shape = 25, size = 2) +  geom_line(aes(y = O_1_5_QO,col = "O 1-5 years > 0")) + geom_point(aes(y = Q_1_5_QO,col = "Q 1-5 years > 0"), fill = "magenta", shape = 22, size = 2) +  geom_line(aes(y = Q_1_5_QO,col = "Q 1-5 years > 0"))+ scale_color_manual( values =c ("blue","magenta"))+labs(title = "Mother's Labor Force Participation", subtitle = "1996 to 2010", x = "Year", y = "Mothers Employed") + scale_x_continuous(breaks=seq(1996, 2010, 1))

QO_Plot

```

```{r}
Q_1_5_Earn  <- Combinedprcf %>% 
  filter (Q == 1) %>%
  group_by(YEAR99) %>% 
  summarise(Q_1_5_Earn = weighted.mean(EARNG42,ICSWT26)) 
  
  ROC_1_5_Earn  <- Combinedprcf %>% 
  filter (Q == 0) %>%
  group_by(YEAR99) %>% 
  summarise(ROC_1_5_Earn = weighted.mean(EARNG42,ICSWT26))
  

  Earn <- left_join(Q_1_5_Earn, ROC_1_5_Earn, by='YEAR99') 
  
  Earn_Plot <- ggplot(data = Earn, aes(x=YEAR99))+ geom_point(aes(y = ROC_1_5_Earn,col = "RoC 1-5 years > 0"), fill = "blue", shape = 25, size = 2) + geom_line(aes(y = ROC_1_5_Earn,col = "RoC 1-5 years > 0")) + geom_point(aes(y = Q_1_5_Earn,col = "Q 1-5 years > 0"), fill = "magenta", shape = 22, size = 2) + geom_line(aes(y = Q_1_5_Earn,col = "Q 1-5 years > 0")) + scale_color_manual( values = c( "magenta","blue")) + labs(title = "Mother's Annual Earned Income", subtitle = "1996 to 2010", x = "Year", y = "Earned Income") + scale_x_continuous(breaks=seq(1996, 2010, 1)) 

    
Earn_Plot
```

```{r}
Q_1_5_Earn  <- Combinedprcf %>% 
  filter (Q == 1) %>%
  group_by(YEAR99) %>% 
  summarise(Q_1_5_EarnQO = weighted.mean(EARNG42,ICSWT26)) 
  
  O_1_5_Earn  <- Combinedprcf %>% 
  filter (O == 1) %>%
  group_by(YEAR99) %>% 
  summarise(O_1_5_EarnQO = weighted.mean(EARNG42,ICSWT26))
  

  EarnQO <- left_join(Q_1_5_Earn, O_1_5_Earn, by='YEAR99') 
  
  EarnQO_Plot <- ggplot(data = EarnQO, aes(x=YEAR99))+ geom_point(aes(y = O_1_5_EarnQO,col = "O 1-5 years > 0"), fill = "blue", shape = 25, size = 2) + geom_line(aes(y = O_1_5_EarnQO,col = "O 1-5 years > 0")) + geom_point(aes(y = Q_1_5_EarnQO,col = "Q 1-5 years > 0"), fill = "magenta", shape = 22, size = 2) + geom_line(aes(y = Q_1_5_EarnQO,col = "Q 1-5 years > 0")) + scale_color_manual( values = c( "blue","magenta")) + labs(title = "Mother's Annual Earned Income", subtitle = "1996 to 2010", x = "Year", y = "Earned Income") + scale_x_continuous(breaks=seq(1996, 2010, 1))

    
EarnQO_Plot
```

```{r}
#Regression



summary(lm(Y3~Q+I1+Q*I1,data=Combinedprcf,weights=ICSWT26))


summary(lm(Y3~Q+I1+Q1999+Q2000+Q2001+Q2002+Q2003+Q2004+Q2005+Q2006+Q2007+Q2008+Q2009+Q2010,data=Combinedprcf,weights=ICSWT26))

summary(lm(EARNG42~Q+I1+Q*I1,data=Combinedprcf,weights=ICSWT26))


summary(lm(EARNG42~Q+I1+Q1999+Q2000+Q2001+Q2002+Q2003+Q2004+Q2005+Q2006+Q2007+Q2008+Q2009+Q2010,data=Combinedprcf,weights=ICSWT26))



```
```{r}
newtable <- Combinedprcf %>% filter(HLEVEG18 <= 6 | HLEVEG18 == 97)
```


```{r}
newtable2 <- Combinedprcf %>% filter(HLEVEG18 > 6 & HLEVEG18 != 97)
```
```

```{r}

summary(lm(Y3~Q+I1+Q*I1,data=newtable,weights=ICSWT26))

summary(lm(Y3~Q+I1+Q1999+Q2000+Q2001+Q2002+Q2003+Q2004+Q2005+Q2006+Q2007+Q2008+Q2009+Q2010,data=newtable,weights=ICSWT26))

summary(lm(EARNG42~Q+I1+Q*I1,data=newtable,weights=ICSWT26))

summary(lm(EARNG42~Q+I1+Q1999+Q2000+Q2001+Q2002+Q2003+Q2004+Q2005+Q2006+Q2007+Q2008+Q2009+Q2010,data=newtable,weights=ICSWT26))


```

```{r}

summary(lm(Y3~Q+I1+Q*I1,data=newtable2,weights=ICSWT26))

summary(lm(Y3~Q+I1+Q1999+Q2000+Q2001+Q2002+Q2003+Q2004+Q2005+Q2006+Q2007+Q2008+Q2009+Q2010,data=newtable2,weights=ICSWT26))

summary(lm(EARNG42~Q+I1+Q*I1,data=newtable2,weights=ICSWT26))

summary(lm(EARNG42~Q+I1+Q1999+Q2000+Q2001+Q2002+Q2003+Q2004+Q2005+Q2006+Q2007+Q2008+Q2009+Q2010,data=newtable2,weights=ICSWT26))

```

```{r}
summary(lm(Y3~O+I1+O*I1,data=Combinedprcf,weights=ICSWT26))


summary(lm(Y3~O+I1+O1999+O2000+O2001+O2002+O2003+O2004+O2005+O2006+O2007+O2008+O2009+O2010,data=Combinedprcf,weights=ICSWT26))

summary(lm(EARNG42~O+I1+O*I1,data=Combinedprcf,weights=ICSWT26))


summary(lm(EARNG42~O+I1+O1999+O2000+O2001+O2002+O2003+O2004+O2005+O2006+O2007+O2008+O2009+O2010,data=Combinedprcf,weights=ICSWT26))
```

```{r}
summary(lm(Y3~O+I1+O*I1,data=newtable,weights=ICSWT26))


summary(lm(Y3~O+I1+O1999+O2000+O2001+O2002+O2003+O2004+O2005+O2006+O2007+O2008+O2009+O2010,data=newtable,weights=ICSWT26))

summary(lm(EARNG42~O+I1+O*I1,data=newtable,weights=ICSWT26))


summary(lm(EARNG42~O+I1+O1999+O2000+O2001+O2002+O2003+O2004+O2005+O2006+O2007+O2008+O2009+O2010,data=newtable,weights=ICSWT26))

```

```{r}
summary(lm(Y3~O+I1+O*I1,data=newtable2,weights=ICSWT26))


summary(lm(Y3~O+I1+O1999+O2000+O2001+O2002+O2003+O2004+O2005+O2006+O2007+O2008+O2009+O2010,data=newtable2,weights=ICSWT26))

summary(lm(EARNG42~O+I1+O*I1,data=newtable2,weights=ICSWT26))


summary(lm(EARNG42~O+I1+O1999+O2000+O2001+O2002+O2003+O2004+O2005+O2006+O2007+O2008+O2009+O2010,data=newtable,weights=ICSWT26))
```

